prolfqua - An R-package for Proteomics Differential Expression Analysis.

### 2022-05-19 inst/MyArticle/paper.Rmd
fix formulas with CP.

$$
z = \frac{x - \bar{x}}{S} \sim \frac{x - \tilde{x}}{\tilde{S}}
$$

Because we need to estimate the protein fold-changes on the original scale, we have to multiply the $z$-score by the average variance of all the $N$ samples in the experiment.

$$
z' = z \times 1/N\sum_{i=1}^N S_i
$$

@@

Given a linear model $y = \beta X$, we can compute the difference between two groups $\beta_{c}$ by a linear combination $c$ of linear model parameters $\beta$. $c$ is vector with as many elements as there are coefficients in the linear model. If $c$ has $0$ for one or more of its rows, then the corresponding coefficient in $\beta$ is not involved in determining the contrast [@ph525xseries].

The difference estimate $\beta_c$, is given by:

\begin{eqnarray} 
\hat{\beta_{c}} &=& \sum l\beta 
\end{eqnarray}

@@

\begin{eqnarray} 
\textrm{var} \hat\beta_c &=& l\sigma^2 (X^T X)^{-1} l^T
\end{eqnarray}

@@

The package prolfqua provides function to determine the vector of $parameter$ weights $c$, from a contrast specification:

- `<contrast name>` = `<factor><level_1> - <factor><level_2>`

@@

- `<contrast name>` = `<factor_1><subgroup>:<factor_2><level_1>` - `<factor_1><subgroup>:<factor_2><level_2>`

where `<factor_x>` is the name of the explanatory variable, and `<level_x>` are group labels.

@@

When computing differences among two groups $a$ and $b$, we will use the group mean $\bar{a}$ or $\bar{b}$ estimated from the data, or if no observations are present we use $A_{LOD}$. If there are no observations in group $b$ then

$$
\Delta_{a,b} = 
\begin{cases}
\bar{a} - A_{LOD} & \text{if} ~~ \bar{a} > A_{LOD}\\
0  &\text{if} ~~ \bar{a} < A_{LOD}.
\end{cases}
$$

>>>>

\begin{eqnarray}
z = \frac{x - \tilde{x}}{\tilde{S}}
\end{eqnarray}

Because we need to estimate the protein fold-changes on the original scale, we have to multiply the $z$-score by the average variance of all the $n$ samples in the experiment.

\begin{eqnarray} 
z' = z \cdot \frac{1}{n}\sum_{i=1}^n S_i
\end{eqnarray}

@@

Given a linear model $y = \beta X$, we can compute the difference between two groups $\beta_{c}$ by a linear combination $c$ of linear model parameters $\beta$. $c$ is a column vector with as many elements as there are coefficients in the linear model. If $c$ has $0$ for one or more of its rows, then the corresponding coefficient in $\beta$ is not involved in determining the contrast [@ph525xseries].

The difference estimate $\beta_c$, is given by the dot product:

\begin{eqnarray} 
\hat{\beta_{c}} &=& c^T \beta 
\end{eqnarray}

@@

\begin{eqnarray} 
\textrm{var} \hat\beta_c &=& c\sigma^2 (X^T X)^{-1} c^T
\end{eqnarray}

@@

The package prolfqua provides function to determine the vector of $parameter$ weights $c$, from a contrast specification string:

```{r eval=FALSE, echo=TRUE}
c("contrast_name" = "factorlevel_1 - factorlevel_2")
```

@@

```{r eval=FALSE, echo=TRUE}
c("contrast_name" = "`factor_1level_a:factor_2level_1` - `factor_1level_a:factor_2level_2`")

```
where `factor_x` is the name of the explanatory variable, and `level_x`  are group labels.

@@

When computing differences $\Delta$ among two groups $a$ and $b$, we will use the group mean $\bar{a}$ or $\bar{b}$ estimated from the data, or if no observations are present in a group we use $A_{LOD}$, e.g., If there are no observations in group $b$ then

$$
\Delta = 
\begin{cases}
\bar{a} - A_{LOD} & \text{if} ~~ \bar{a} > A_{LOD}\\
0  &\text{if} ~~ \bar{a} < A_{LOD}.
\end{cases}
$$
